The pollination trade-off

### 2019-06-17 paper/supp-info.Rmd
Add list of manual corrections to supp. info

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
options(xtable.comment = FALSE, 
        xtable.caption.placement = 'bottom',
        xtable.size = 'small',
        booktabs = TRUE, 
        knitr.kable.NA = "-")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
options(xtable.comment = FALSE, 
        xtable.caption.placement = 'bottom',
        xtable.size = 'small',
        booktabs = TRUE, 
        knitr.kable.NA = "-")
library(dplyr)
```

```{r tab-manual-name-corrections}
loadd(spp, manual_name_corrections)
manual_name_corrections %>%
  inner_join(spp, by = c("queried_sp_name" = "sp_name")) %>%
  distinct(queried_sp_name, sp_name, guild) %>%
  filter(!is.na(sp_name)) %>%
  arrange(guild, queried_sp_name, sp_name) %>%
  mutate(sp_name = tidyr::replace_na(sp_name, "no replacement found"), 
         sp_name = kableExtra::cell_spec(sp_name, italic = TRUE), 
         guild = if_else(guild == "pla", "plant", "pollinator")) %>%
  knitr::kable(caption = "Manually corrected canonnical names. More than one correct name have been included when an accepted/valid synonym the cannonical name exists.", 
               col.names = c("incorrect name", "corrected name", "guild"),
               booktabs = TRUE, 
               escape = F) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::collapse_rows(1, latex_hline = "none", valign = "top")
```

```{r eval = FALSE, tab-sp-synonym-reasons}
sp_with_synonyms %>%
  filter(!is.na(itis_reason)) %>%
  group_by(queried_sp_name) %>%
  summarise(itis_reason = first(itis_reason)) %>%
  group_by(itis_reason) %>%
  count(sort = T) %>%
  knitr::kable("latex", 
               col.names = c("reason of species alternative name", "n"), 
               caption = "tablesita", 
               booktabs = TRUE) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::collapse_rows(columns = 1)
```
